Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-23 robdml.tex
tex

% for problem 2
\oo{[2. Gradual Adversary]}
The expectation of hardness will decrease during the training process,
compared to that from the beginning phase.

@@

% evaluation and conclusion
\oo{[experimetal evaluations]}
To validate the effectiveness of the proposed method, we conduct experiments
on three commonly used dataset, namely CUB-200-2011, Cars-196, and Stanford
Online Product. Our conclusions are:
%
(1) Triplet sampling strategy is vital for adversarial training of tripet-loss
based DML models.
%
\oo{the results suggest that}

% contributions
In brief, our contribusions include:
%
\begin{enumerate}[noitemsep]
	%
	\item {\textit{Hardness Manipulation}} is proposed for the adversarial
		training of triplet-based deep metric learning models, which avoids
		model collapse in the typical min-max adversarial training setting.
		The proposed method achieves higher adversarial robustness compared to
		the state-of-the-art, and is more computationally efficient.
		%
		This method makes min-max training feaisble, and hence the incorporation
		into free adversarial training and boost learning efficiency.
		%
		(initial condition)
		%
	\item \textit{Gradual Adversary} is proposed to dynamically adjust the
		destination hardness less for Hardness Manipulation during the
		adversarial training process in order to balance the metric learning
		and adversarial learning.
		%
		(terminal condition)
		%
	\item Inter-ID structure constraint. ((aa~p) + (pp~a))/2
		(cross-id repelling)
		existing methods only care inter-class separation, but not
		intra-class (inter-id) separation, because we may get a 6-element
		set (a,a~,p,p~,n,n~) from the original triplet.
		%
\end{enumerate}

The proposed method overwhelmingly outperforms the state-of-the-art defense
in terms of robustness, training cost, as well as the penalty on benign
example retrieval.

>>>>

To this end, we propose Graduate Adversary, a family of pseudo-hardness
functions which can be used as the \emph{destination} hardness in HM.
%
Any function that leads to a relatively weak adversary in the early training
phase, and a relatively strong adversary in the late training phase belongs to
this family.
%
As an example, we design a ``Simple Graduate Adversary'' (SGA) pseudo-hardness
function as the linearly scaled negative triplet margin, incorporating a strong
assumption that the \emph{destination} hardness should remain Semihard.
%
Empirical observation will show the advantage of such pseudo-hardness
functions.

@@

% evaluation and conclusion
We conduct experiments
on three commonly used DML dataset, namely CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196}, and Stanford
Online Product~\cite{sop}.
%
The proposed method overwhelmingly outperforms the state-of-the-art defense
in terms of robustness, training cost, as well as the penalty on benign
example retrieval.
%
Our conclusions are:
%
(1) Triplet sampling strategy is vital for adversarial training of tripet-loss
based DML models.
%
\oo{...}

% contributions
In brief, our contribusions include:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) is proposed as a flexible tool
		to create adversarial triplets with increased hardness for
		subsequent adversarial training.
		%
		It is more efficient than previous adversarial training methods of DML.
		%
	\item \textit{Gradual Adversary} is proposed as a family of pseudo-hardness
		functions for \emph{Hardness Manipulation}, which can balance the
		training objectives during the training process.
		%
		A linear function named Simple Graduate Adversary (SGA) is designed as
		an example.
		%
	\item \oo{TODO} Inter-ID structure constraint. ((aa~p) + (pp~a))/2
		(cross-id repelling) existing methods only care inter-class separation,
		but not intra-class (inter-id) separation, because we may get a
		6-element set (a,a~,p,p~,n,n~) from the original triplet.
		%
\end{enumerate}
